Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-06-18 article.tex
LNCS 12 pages + appendix

$\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ can be solved by means by the following relations:

@@

	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is a descent element then:

	$$
	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}=
	\begin{cases}
			\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}
				& \text{if $\pmotif[i]$ is not underlined } \\
				& \text{ and $\pmotif[i]$ is not overlined} \\
			\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}
				& \text{if $\pmotif[i]$ is not underlined } \\
				& \text{ and $\overline{\pmotif[i](\pmotif[i]+1)}$ or ${\pmotif[i]}^\urcorner$}\\
				& \text{ and $\ptext[j]=\ub$} \\
			\PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
				& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
				& \text{ and $\overline{\pmotif[i](\pmotif[i]+1)}$ or ${\pmotif[i]}^\urcorner$}\\
				& \text{ and $\ptext[j]=\ub$} \\
			\PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
				& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
				& \text{ and $\pmotif[i]$ is not overlined} \\
			false & \text{otherwise}
	\end{cases}
	$$	
	The same remark as the last case holds.

@@

		\item If $\sigma[i]$ is an descent element, then remark that 
		every problem 
		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ occurs in element $\ub$ thus it is enough to require that $\ub=n_{\ptext}$.
		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if not, then there exists an descent element $\sigma[i']$, $i'<i$ and by definition $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the maximal element. As a consequence every problem $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$, $\dots$, $\PM{\pbmotif}{\ptext}{*}{*}{i-1}{*}$ is called with ascent elements thus every problem 
		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ has same upper bound as $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$ thus for every $\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$,
		$\ub=n_{\ptext}$.

@@

	\item  If $\overline{\pmotif[i]\pmotif[i']}$,  (which implies that $\pmotif[i']=\pmotif[i]+1$) then if $\pmotif[i]$ occurs in $\ptext[j]$ then $\pmotif[i']$ must occur in $\ptext[j]+1$.
		\begin{itemize}

>>>>

$\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}$ can be solved according to  
the following relations:

@@

	\item If $\ptext[j] \in [\lb,\ub]$ and $\pmotif[i]$ is a descent element then:
	$$
	\PM{\pbmotif}{\ptext}{\lb}{\ub}{i}{j}=
	\begin{cases}
			\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}
				& \text{if $\pmotif[i]$ is not underlined } \\
				& \text{ and $\pmotif[i]$ is not overlined} \\
			\bigcup_{j<k} \PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{k}
				& \text{if $\pmotif[i]$ is not underlined } \\
				& \text{ and $\overline{\pmotif[i](\pmotif[i]+1)}$ or ${\pmotif[i]}^\urcorner$}\\
				& \text{ and $\ptext[j]=\ub$} \\
			\PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
				& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
				& \text{ and $\overline{\pmotif[i](\pmotif[i]+1)}$ or ${\pmotif[i]}^\urcorner$}\\
				& \text{ and $\ptext[j]=\ub$} \\
			\PM{\pbmotif}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
				& \text{if $\underline{\pmotif[i]\pmotif[i+1]}$ } \\
				& \text{ and $\pmotif[i]$ is not overlined} \\
			false & \text{otherwise}
	\end{cases}
	$$	
	The same remark as the last case holds.

@@

		\item If $\sigma[i]$ is an descent element, then remark that 
		every problem 
		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ is true if $\sigma[i]$ occurs 
		in element $\ub$ thus it is enough to require that $\ub=n_{\ptext}$.
		Now remark that $\sigma[i]$ is the leftmost descent element, indeed if it is not
		then there exists an descent element $\sigma[i']$, $i'<i$ and by definition 
		$\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the maximal
		element. 
		As a consequence every problem 
		$\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$, $\dots$, 
		$\PM{\pbmotif}{\ptext}{*}{*}{i-1}{*}$ 
		is called with ascent elements thus every problem 
		$\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$ 
		has same upper bound as $\PM{\pbmotif}{\ptext}{1}{n_{\ptext}}{1}{*}$ 
		thus for every $\PM{\pbmotif}{\ptext}{*}{\ub}{i}{*}$,
		$\ub=n_{\ptext}$.

@@

	\item  If $\overline{\pmotif[i]\pmotif[i']}$
	(which implies that $\pmotif[i']=\pmotif[i]+1$), 
	then if $\pmotif[i]$ occurs in $\ptext[j]$ 
	then $\pmotif[i']$ must occur in $\ptext[j]+1$.
		\begin{itemize}
